### 2017-03-13 CO750-ApproximationAlgorithmsTopics/assignments/assignment_02.tex
starting 4

>>>>

%Q4
\section{}
\paragraph{}
Consider the packing problem $(P)$: Let $U$ be a set of elements. Let $\cS$ be a non-empty family of sets $S\subseteq U$. The goal is to find a subcollection of $\cS$ of maximum cardinality, subject to the constraint that each element is contained in at most $1$ set.
\paragraph{}
We can write a linear programming relaxation for $(P)$, denoted $(LP)$ as
\begin{align*}
\max \sum_{S\in\cS} x_S\ & \\
\text{s.t.} \sum_{S:e\in S} x_S &\leq 1 &\forall e\in U \\
x&\geq 0.
\end{align*}
Let $k = \max_{S\in \cS} \{ |S|\}$.
%pa
\subsection*{a}
